Alex Popescu - Final Stats

### 2024-01-31 Data & Scripts/Alex Popescu - Final Stats.Rmd
Jan 31
Gotta go to work

##BOUT Model - Head Down

@@

sjPlot::tab_model(BOUT.MOD.HU
                  , pred.labels = labs.bout.2
                  , show.re.var = T
                  , show.se = T
                  , show.stat = T
                  , digits = 4
                  , title = "Head Up"
                  , dv.labels = " Effects on alert bout duration")+
  theme_sjplot(base_family = "serif")

@@

tab_model(PTWY.MODELS
          , pred.labels = labs.ptwy
                  , show.re.var = T
                  , show.se = T
                  , show.stat = T
                  , digits = 4
                  , title = ""
                  , dv.labels = c("Foraging to Alert"
                                  , "Foraging to Peck"
                                  , "Alert to Foraging"
                                  , "Peck to Alert")
          )+
  theme_sjplot(base_family = "serif")
```
```{r Save PTWY Table, include = F}
webshot("PTWY_Table.html", "PTWY_Table.png")
```

>>>>

## BOUT Model - Head Down

@@

sjPlot::tab_model(BOUT.MOD.HU
                  , pred.labels = labs.bout.2
                  , show.re.var = T
                  , show.se = T
                  , show.stat = T
                  , digits = 4
                  , title = "Head Up"
                  , dv.labels = " Effects on alert bout duration")

@@

tab_model(PTWY.MODELS
          , pred.labels = labs.ptwy
                  , show.re.var = T
                  , show.se = T
                  , show.stat = T
                  , digits = 4
                  , title = ""
                  , dv.labels = c("Foraging to Alert"
                                  , "Foraging to Peck"
                                  , "Alert to Foraging"
                                  , "Peck to Alert")
          )
```
```{r Save PTWY Table, include = F}
webshot("PTWY_Table.html", "PTWY_Table.png")
```
